Checkpoint 3

### 2020-04-22 Checkpoint3.Rmd

---
title: "Checkpoint 3"
author: ""
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
  - \usepackage{tabularx}
output:
  pdf_document: default
  html_document: default
abstract: ""
---

>>>>

---
title: "Checkpoint 3"
author: ""
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc:true
    toc_float:true
---
```{r}
library(dplyr)
```

# Data
```{r}
save(states_cases_data, file = 'states_cases_data.RData')
dim(states_cases_data)
names(states_cases_data)
head(states_cases_data)
summary(states_cases_data)

```

# Quinn Tries to Plot some stuff
```{r}
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)

##Map for Positive Cases (Need to figure out how to make scale more feasible)
plot_usmap(regions = "state", data=states_cases_data, values = "positive")+
    labs(title = "Positive COVID-19 Tests") + 
    theme(panel.background = element_rect(colour = "black"))+
    scale_fill_continuous(low = "white", high ="darkblue", 
                          name = "# of Positive Cases",label = scales::comma,
                          limits = c(0,1000)) + 
    theme(legend.position = "right") +facet_wrap(~date)

##Map for Positive Cases but only for East Coast 
plot_usmap(data = states_cases_data, values = "positive", include =  c(.south_atlantic, .mid_atlantic, .new_england ), color = "orange", labels=TRUE) + 
  scale_fill_continuous( low = "white", high = "orange", 
                         name = "Positive cases", label = scales::comma
  ) + 
  theme(legend.position = "right") + 
  theme(panel.background = element_rect(colour = "black")) + 
  labs(title = "US East Coast Positive COVID Cases")

```

```{r}
### HOW DO i FIX THE SCALE SO THAT OUTLIARS WONT MESS EVERYTHING UP???
library(statebins)
statebins(state_data = states_cases_data, state_col = "state",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Reds", font_size = 3,breaks =4,
                     legend_title="# of Positive COVID-19 Cases",
                 labels = c("0-5000", "5000-10000", "10000-20000", "20000-35000"))
```
